Corpus Analysis

### 2020-08-24 inst/analysis/corpus-stage2.Rmd
Update the runnable-code-metadata to include per program data

```{r process runnable code}
runnable_code <- 
  runnable_code_raw %>%
  filter(language=="R") %>%
  select(package, path, code, files) %>%
  pivot_wider(
    names_from=path, 
    values_from=c(code, files), 
    values_fill=list(code=0, files=0)
  ) %>%
  # TODO we have old version of tidyr, names_glue is missing, so have to rename manually
  rename(
    runnable_code_examples=code_examples,
    runnable_code_tests=code_tests,
    runnable_code_vignettes=code_vignettes,
    runnable_files_examples=files_examples,
    runnable_files_tests=files_tests,
    runnable_files_vignettes=files_vignettes,
  ) %>%
  mutate(
    runnable_code=runnable_code_examples+runnable_code_tests+runnable_code_vignettes,
    runnable_files=runnable_files_examples+runnable_files_tests+runnable_files_vignettes
  ) %>%
  select(
    package,
    runnable_code,
    runnable_files,
    everything()
  )
```

>>>>

```{r process runnable code}
runnable_code <- 
  runnable_code_raw %>%
  filter(language=="R") %>%
  mutate(path=case_when(
    str_starts(filename, "./examples") ~ "examples",
    str_starts(filename, "./tests") ~ "tests",
    str_starts(filename, "./vignettes") ~ "vignettes"
  )) %>%
  group_by(package, path) %>%
  summarise(files=n(), code=sum(code)) %>%
  pivot_wider(
    names_from=path, 
    values_from=c(code, files), 
    values_fill=list(code=0, files=0)
  ) %>%
  # TODO we have old version of tidyr, names_glue is missing, so have to rename manually
  rename(
    runnable_code_examples=code_examples,
    runnable_code_tests=code_tests,
    runnable_code_vignettes=code_vignettes,
    runnable_files_examples=files_examples,
    runnable_files_tests=files_tests,
    runnable_files_vignettes=files_vignettes,
  ) %>%
  mutate(
    runnable_code=runnable_code_examples+runnable_code_tests+runnable_code_vignettes,
    runnable_files=runnable_files_examples+runnable_files_tests+runnable_files_vignettes
  ) %>%
  select(
    package,
    runnable_code,
    runnable_files,
    everything()
  )
```
